---
title: "Final"
author: "Anya Harrington, Allison Kriens, Anna Koblitz, Emily Mauch"
date: "4/18/2022"
output:
  html_document: default
  pdf_document: default
  word_document: default
---



### Background


-Information from the top 1000 movies was pulled from the Internet Movies Database (IMDb)
  - Movie Title
  - Year 
  - Genre 
  - Director(s)
  - 2 Leading Actors
  - Number of Votes (Determined Rank)
  - Gross
  
  
- Movie rank was determined via popular vote 


-Popular vote is determined by how many people visit the IMDb page for a specific movie each week (Focuses on recent popular movies)


- User rank is determined by how IMDb users rank specific movies (Focuses on the most popular movies of all time)

  
- Goal: 
  -Create a actor network which connects based on movie costars
  -Find the Hanky Number (The number of actors between a specific person and Tom Hanks)  
<br>
<br>
```{r Packages to install, eval=FALSE, include=FALSE}

##installing packages 

#install.packages("naniar")
#install.packages("igraph")
#install.packages("ggraph")
#install.packages("visNetwork")
#install.packages('DT')


```

```{r Packages to open, include=FALSE}
##loading libraries
library(tidyverse)
library(rvest) 
library(naniar)
library(igraph)
library(ggraph)
library(visNetwork)            
library(DT)
library(plotly)
```


```{r include=FALSE}
#Function : data
#Input : a url to a 50 of the top 1000 movies. Selects and formats movie rank, title, year, directors/actors, votes/gross
#Output : a data frame of 50 movies with variables above

data <- function(x){
  html <- read_html(x)
  top_50 <- html_nodes(html, ".sort-num_votes-visible , .text-muted+ p , .genre , .unbold , .lister-item-header a")
  a <- html_text(top_50) 
  b <- str_replace_all(a, "[\r\n]" , "")
  c <- str_squish(b)
  d <- gsub("[()]", "", c)   
  x <- str_replace_all(d, "[I]+", "")
  as.data.frame(matrix(x, ncol = 6, nrow = 50, byrow= TRUE))
}

##assiging urls
a <- data("https://www.imdb.com/search/title/?groups=top_1000&start=1")
b <- data("https://www.imdb.com/search/title/?groups=top_1000&start=51&ref_=adv_nxt")
c <- data("https://www.imdb.com/search/title/?groups=top_1000&start=101&ref_=adv_nxt")
d <- data("https://www.imdb.com/search/title/?groups=top_1000&start=151&ref_=adv_nxt")
e <- data("https://www.imdb.com/search/title/?groups=top_1000&start=201&ref_=adv_nxt")
f <- data("https://www.imdb.com/search/title/?groups=top_1000&start=251&ref_=adv_nxt")
g <- data("https://www.imdb.com/search/title/?groups=top_1000&start=301&ref_=adv_nxt")
h <- data("https://www.imdb.com/search/title/?groups=top_1000&start=351&ref_=adv_nxt")
i <- data("https://www.imdb.com/search/title/?groups=top_1000&start=401&ref_=adv_nxt")
j <- data("https://www.imdb.com/search/title/?groups=top_1000&start=451&ref_=adv_nxt")
k <- data("https://www.imdb.com/search/title/?groups=top_1000&start=501&ref_=adv_nxt")
l <- data("https://www.imdb.com/search/title/?groups=top_1000&start=551&ref_=adv_nxt")
m <- data("https://www.imdb.com/search/title/?groups=top_1000&start=601&ref_=adv_nxt")
n <- data("https://www.imdb.com/search/title/?groups=top_1000&start=651&ref_=adv_nxt")
o <- data("https://www.imdb.com/search/title/?groups=top_1000&start=701&ref_=adv_nxt")
p <- data("https://www.imdb.com/search/title/?groups=top_1000&start=751&ref_=adv_nxt")
q <- data("https://www.imdb.com/search/title/?groups=top_1000&start=801&ref_=adv_nxt")
r <- data("https://www.imdb.com/search/title/?groups=top_1000&start=851&ref_=adv_nxt")
s <- data("https://www.imdb.com/search/title/?groups=top_1000&start=901&ref_=adv_nxt")
t <- data("https://www.imdb.com/search/title/?groups=top_1000&start=951&ref_=adv_nxt")
##binding data sets together 
top <- rbind(a,b,c,d,e,f,g,h,i,j,k,l,m,n,o,p,q,r,s,t)
```



```{r echo=FALSE, warning=FALSE}
#Formatting data frame 
##selected genre, actors, votes, title, year, director, gross

top <- top %>% separate(V1, c("Rank", NA), sep="[.]") %>%
  separate(V4, c("Genre1", "Genre2", "Genre3"), sep="[,]")%>%
  separate(V5, c("Director", "Actor"), sep = "[|]") %>%
  separate(Director, c(NA, "Director"), sep = "[:]") %>%
  separate(Actor, c(NA, "Actors"), sep = "[:]")%>%
  separate(V6, c("Votes", "Gross"), sep = "[|]", extra="merge")  %>%
  separate(Votes, c(NA, "Votes"), sep = "[:]") %>% 
  rename("Title" = "V2", "Year"="V3") %>% 
  separate(Actors, c("Actor1", "Actor2", "Actor3", "Actor4"), sep = "[,]") %>%
  separate(Gross, c("Gross1", "Gross2"), sep="[:]") %>% 
  separate(Gross2, c("Gross2", "Gross3"), sep = "[|]") %>% 
  separate(Gross2, c("Gross2", "Gross4"), sep = "[#]") %>%
  select("Rank":"Votes", "Gross2")%>%
  rename("Gross" = "Gross2") %>%
  replace_with_na(replace = list(Gross = ""))

```

```{r, echo=FALSE}
#Producing data frame "actors". Contains 3 rows per movie that correlates each actor in the movie to the "top" actor. Modified top for graphing 
#Format must be "Actor1", "Actor2" then "title"
top_longer <- top  %>% 
  select(Title, Actor1:Actor2)
col_order <- c("Actor1", "Actor2", "Title")
top_longer <- top_longer[, col_order]

#Producing Data frame "Actors" contains just actors and removes all duplicates. Needed for graphing function 
Actors <- top %>% 
  select(Actor1:Actor2, Title) %>%  
  pivot_longer(cols= "Actor1":"Actor2",names_to= "Remove", values_to = 'Actor') %>% 
  select(-"Remove")
#Removes duplicate actors
Actors <- distinct(Actors, Actor)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Producing actor network plot 
#Input:
  #d: data frame with top actor linked the 2nd, 3rd and 4th actors divided out by movie
  #vertices: Just a list of all of the actors in movies 
  #direct = FALSE due to multiple actors in multiple movies and aren't directed linked to every other actor 
#Output: list of actors and who they are related to 
actorNetwork <- graph_from_data_frame(d=top_longer, vertices=Actors, directed=FALSE)


#Graph with all actors, not including names, visualize all connections
ggraph(actorNetwork)+
  geom_edge_link(alpha = 0.5) +     
  geom_node_point(size = 0.5, shape = 21, stroke = 1,
                  fill = 'white', color = 'black') +
  geom_node_text(aes(label=NA), size = 3) +
  labs(title = "Top 1000 Movies Actor Network")+
  theme_void()

#Graph with all actors
par(mar = c(0,0,0,0))
ll <- layout.auto(actorNetwork)


```

### Takeaways from static network of all actors:

-Very many actors with only one or two connections, this led to many difficulties in forming a cohesive web.



### Brief Methods:


-Scrape data


-Using R network and graphing functions produce plot.


-This plot was fairly automated using functions already built into R. 
  
    
    
<br>
<br>


```{r echo=FALSE, message=FALSE, warning=FALSE}
##Selecting actor1 actor 2 and title from top dataset
Actors <- top %>% 
  select(Actor1:Actor2, Title) %>%  
  pivot_longer(cols= "Actor1":"Actor2",names_to= "Remove", values_to = 'Actor') %>% 
  select(-"Remove")

#View(Actors)
##selecting only the actors
actorswide <- top %>% 
  select(Actor1:Actor2)
##creating a list of unique actors/ removing duplicate
distinctactors <- top %>% 
  select(Actor1:Actor2) %>%  
  pivot_longer(cols= "Actor1":"Actor2",names_to= "Remove", values_to = 'Actor') %>%    select(-"Remove")
#Removes duplicate actors
distinctactors <- distinct(distinctactors, Actor)


##assigning each distict actor an ID, merging as neccessary, to end up with a dataframe with only actor 1 ID and Actor 2 ID for use in building links later on 
distinctactors$ID <- seq(1:1486)
distinctactors$Actor2 <- distinctactors$Actor
##setting colnames
colnames(distinctactors) <- c("Actor1", "ID", "Actor2")
#View(distinctactors)
#merging and deleting unneeded cols
merged1 <- merge(distinctactors, actorswide, by="Actor1")
mergedint <-merged1[,-3]
colnames(mergedint) <- c("Actor1", "ID", "Actor2")
mergedint2 <- merge(distinctactors, mergedint, by="Actor2")
##formating link dataframe
finalmerged <- select(mergedint2, -c(1,2,4))
colnames(finalmerged) <- c("Source", "Target")
#View(finalmerged)
hugenodes <- select(distinctactors, c(1,2))
colnames(hugenodes) <- c("Actor", "ID")


##assigning nodes and links
huge_links <- finalmerged
huge_nodes <- hugenodes


##creating network
huge_network <- graph_from_data_frame(huge_links,
                                    vertices= huge_nodes$ID,
                                    directed = F)


#### Creating nodes and assigining lables and titles for future use 
huge_nodes <- huge_nodes %>%
  mutate(label = Actor) %>% 
  mutate(title = Actor) %>% 
  mutate(degree= degree(huge_network)) %>% 
  mutate(value = degree)

huge_links <- huge_links %>% 
  mutate(betweenness= edge_betweenness(huge_network)) %>% 
  mutate(value= betweenness)


##creating edges from the source to target actor 
edges <- data.frame(from = huge_links$Source, to=huge_links$Target)
##removing a coloumn
finalnodes<- as.data.frame(huge_nodes[,-1])
colnames(finalnodes) <- (c("id", "lable", "title", "degree", "value"))
#View(finalnodes)
##removing unnecceary columns and setting coloumn names 
huge_nodes <- as.data.frame(huge_nodes[,-1])
colnames(huge_nodes) <- (c("id", "label", "title", "degree", "value"))

##plotting interactive network
visNetwork(nodes=huge_nodes, edges, main = "Large Network Diagram") %>% 
  visIgraphLayout(layout = "layout_nicely") %>% 
  visOptions(highlightNearest = T, nodesIdSelection = T)

```

### Key takeways from interactive plot of all actors:


-Interactivity is added to get a better grasp on the data set.


-Allows for viewing specific connections and further exploration of data.


### Brief Methods:


-Each actor was assigned a number ID, and these actors formed nodes or dots on the graph.


-Data was manipulated to form a data set with an ID "source" and ID "target" for those who worked together on a film. 

-From there, we were able to produce an interactive plot using determined connections.

<br>
<br>


```{r echo=FALSE, message=FALSE}
##possibly extra example 
## example modified from http://rstudio-pubs-static.s3.amazonaws.com/472488_eaddd648192d41ec9d508267ea592bf9.html

###getting data files, of harry potter characters and relationship connectivity
hp_links <- read_csv("relations.csv")
hp_nodes <- read_csv("characters.csv")
#View(hp_nodes)

##creating network
hp_network <- graph_from_data_frame(hp_links,
                                    vertices= hp_nodes,
                                    directed = F)

## Creating nodes and assigining lables and titles for future use 
hp_nodes <- hp_nodes %>%
  mutate(label = name) %>% 
  mutate(title = name) %>% 
  mutate(degree= degree(hp_network)) %>% 
  mutate(value = degree)
## Creating links for connections
hp_links <- hp_links %>% 
  mutate(betweenness= edge_betweenness(hp_network)) %>% 
  mutate(value= betweenness)


##setting to and from values for edges
edges <- data.frame(from = hp_links$source, to=hp_links$target)


#View(hp_nodes)
#View(hp_links)
##plotting interactive network
visNetwork(nodes=hp_nodes, edges, main = "Harry Potter Network Diagram") %>% 
  visIgraphLayout(layout = "layout_nicely") %>% 
  visOptions(highlightNearest = T, nodesIdSelection = T)


```

### Reasoning Behind Harry Potter Network:


-Due to lack of connectivity in original data set, we decided to explore an extra set of data.


-As it is based upon a series, it is, as expected, more intertwined. 


-This provided us with a good micro example, to move forward with our original data set. 

<br>
<br>

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Producing data frame with just actors with more then one connection
actorswide2 <- tibble(actorswide)
unique_actors1 <- data_frame("actor1" = unique(actorswide2$Actor1)) 
unique_actors1 <- unique_actors1 %>% arrange(actor1)
unique_actors1$connections <- table(actorswide2$Actor1)
unique_actors2 <- data_frame("actor1" = unique(actorswide2$Actor2)) 
unique_actors2 <- unique_actors2 %>% arrange(actor1)
unique_actors2$connections <- table(actorswide2$Actor2)
unique_1<- rbind(anti_join(unique_actors1, unique_actors2, "actor1"), anti_join(unique_actors2, unique_actors1, "actor1")) 
unique_1 <- unique_1 %>% filter(connections == "1")
actorswide2$tf <- actorswide2$Actor1 %in% unique_1$actor1
actorswide2$tf2 <- actorswide2$Actor2 %in% unique_1$actor1
actorswide2 <- actorswide2 %>% filter(tf == FALSE | tf2 == FALSE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Producing data frame with only actors who have more then one connection
Actors_small <- actorswide2 %>% 
  select(Actor1:Actor2) %>%  
  pivot_longer(cols= "Actor1":"Actor2",names_to= "Remove", values_to = 'Actor') %>% 
  select(-"Remove")
Actors_small<- distinct(Actors_small)

#Producing actor network plot 
#Input:
  #d: data frame with top actor linked the 2nd, 3rd and 4th actors divided out by movie
  #vertices: Just a list of all of the actors in movies 
  #direct = FALSE due to multiple actors in multiple movies and aren't directed linked to every other actor 
#Output: list of actors and who they are related to 
actorNetwork_small <- graph_from_data_frame(d=actorswide2, vertices=Actors_small, directed=FALSE)

#Producing static graph with only actors who have more then one connection
ggraph(actorNetwork_small)+
  geom_edge_link(alpha = 0.5) +     
  geom_node_point(size = 0.5, shape = 21, stroke = 1,
                  fill = 'white', color = 'black') +
  geom_node_text(aes(label=NA), size = 3) +
  labs(title = "Network of Actors With More Than One Connection")+
  theme_void()

#Producing graph with only actors who have more then one connection
par(mar = c(0,0,0,0))
ll <- layout.auto(actorNetwork_small)


```

### Key takeaways from static network including actors with more than one connection:


-Reflects same idea as above, but actors who were only connected to their costar have been removed. 
<br>
<br>
<br>

```{r, include=FALSE}
#Adding IDs to actorswide
Actors_small$ID <- seq(1:700)
#ID1
##setiing col names and merging when needed 
colnames(actorswide2) <- c("Actor", "Actor2")
merged1_small <- merge(Actors_small, actorswide2, by="Actor")
#ID2
colnames(merged1_small) <- c("Actor1", "ID1", "Actor")
merged2_small <- merge(Actors_small, merged1_small, by="Actor")
##selecting needed columns
finalmerged_small <- select(merged2_small, c(2,4))
colnames(finalmerged_small) <- c("Source", "Target")

nodes_small <- select(Actors_small, c(1,2))


#View(Actors_small)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
small_links <- finalmerged_small
small_nodes <- nodes_small
#View(small_nodes)
##reproducing the same graph as large network for network of actors with only more than one connection see above comments for needed clarification

##creating network
small_network <- graph_from_data_frame(small_links,
                                    vertices= small_nodes$ID,
                                    directed = F)



small_nodes <- small_nodes %>%
  mutate(label = Actor) %>% 
  mutate(title = Actor) %>% 
  mutate(degree= degree(small_network)) %>% 
  mutate(value = degree)

small_links <- small_links %>% 
  mutate(betweenness= edge_betweenness(small_network)) %>% 
  mutate(value= betweenness)



edges <- data.frame(from = small_links$Source, to=small_links$Target)

finalnodes<- as.data.frame(small_nodes[,-1])
colnames(finalnodes) <- (c("id", "lable", "title", "degree", "value"))
#View(finalnodes)

small_nodes <- as.data.frame(small_nodes[,-1])
colnames(small_nodes) <- (c("id", "label", "title", "degree", "value"))


visNetwork(nodes=small_nodes, edges, main = "Actors With More Than One Connection Interactive Network Diagram") %>% 
  visIgraphLayout(layout = "layout_nicely") %>% 
  visOptions(highlightNearest = T, nodesIdSelection = T)

```



### Key takeaways from interactive network including actors with more than one connection:


-As before, we are able to see more in depth into the true social network using the interactive features.
<br>
<br>

```{r echo=FALSE, message=FALSE, warning=FALSE}
##For a specific genre


##filtering down to only acotrs in drama movies
drama <- top  %>%
  select(Title, Actor1:Actor2, Genre1) %>%
  filter(Genre1 == "Drama")
col_order2 <- c("Actor1", "Actor2", "Title", "Genre1")
drama <- drama[, col_order2]

dramaActors <- top %>%
  select(Actor1:Actor2, Title, Genre1) %>%
  filter(Genre1 == "Drama") %>%
  pivot_longer(cols= "Actor1":"Actor2",names_to= "Remove", values_to = 'Actor') %>%
  select(-"Remove")
dramaActors <- distinct(dramaActors, Actor)



##assigns IDS and repeating steps taken above
dramaActors$ID <- seq(1:510)
dramaActors$Actor2 <- dramaActors$Actor
colnames(dramaActors) <- c("Actor1", "ID", "Actor2")
#View(distinctactors)
mergeddrama1 <- merge(dramaActors, drama, by="Actor1")
mergedint <-mergeddrama1[,-3]
colnames(mergedint) <- c("Actor1", "ID", "Actor2")
mergeddrama2 <- merge(dramaActors, mergedint, by="Actor2")
finalmergeddrama <- select(mergeddrama2, c(3,5))
#View(finalmergeddrama)

colnames(finalmergeddrama) <- c("Source", "Target")
#View(finalmerged)
hugenodesdrama <- select(dramaActors, c(1,2))
colnames(hugenodesdrama) <- c("Actor", "ID")


#View(hugenodesdrama)
#View(finalmergeddrama)



huge_linksdrama <- finalmergeddrama
huge_nodesdrama <- hugenodesdrama


##creating network
huge_networkdrama <- graph_from_data_frame(huge_linksdrama,
                                    vertices= huge_nodesdrama$ID,
                                    directed = F)


##creating nodes
huge_nodesdrama <- huge_nodesdrama %>%
  mutate(label = Actor) %>% 
  mutate(title = Actor) %>% 
  mutate(degree= degree(huge_networkdrama)) %>% 
  mutate(value = degree)
##creating links
huge_linksdrama <- huge_linksdrama %>% 
  mutate(betweenness= edge_betweenness(huge_networkdrama)) %>% 
  mutate(value= betweenness)


##creating edges
edges <- data.frame(from = huge_linksdrama$Source, to=huge_linksdrama$Target)

finalnodesdrama<- as.data.frame(huge_nodesdrama[,-1])
colnames(finalnodesdrama) <- (c("id", "lable", "title", "degree", "value"))
#View(finalnodes)
##nodes 
huge_nodesdrama <- as.data.frame(huge_nodesdrama[,-1])
colnames(huge_nodesdrama) <- (c("id", "label", "title", "degree", "value"))

##interactive network
visNetwork(nodes=huge_nodesdrama, edges, main = "Drama Network Diagram") %>% 
  visIgraphLayout(layout = "layout_nicely") %>% 
  visOptions(highlightNearest = T, nodesIdSelection = T)



```


## Key takeaways from interactive network including actors who acted within the drama genre:


-As a surprise when filtered by genre, we didn't see any more connectivty than we did with the data as a whole.
<br>
<br>
<br>

```{r include=FALSE, message=FALSE, warning=FALSE}
##cacluation bacon score for harry potter dataset, number of connections away for Harry Potter
hp_network <- graph_from_data_frame(hp_links,
                                    vertices= hp_nodes,
                                    directed = F)

small_network <- graph_from_data_frame(small_links,
                                    vertices= small_nodes$ID,
                                    directed = F)


baconhp <- as.data.frame(distances(hp_network, v=V(hp_network)["Harry Potter"], to=V(hp_network), weights=NA))
##taking the transpose as making it a dataframe
baconhp <- as.data.frame(t(baconhp))
baconhp <- tibble::rownames_to_column(baconhp, "Name")
colnames(baconhp) <- c("Name", "Score")

#View(baconhp)
##calculating bacon score for network with more than one connection, had to begin with the ID because of how data was formatted but, this is steps away from Tom Hanks
baconsmallnet <- as.data.frame(distances(small_network, v=V(small_network)["70"], to=V(small_network), weights=NA))

names(baconsmallnet)<- NULL
##adding in IDS
baconsmallnet[nrow(baconsmallnet) + 1,] = seq(1:700)



names(baconsmallnet)<- NULL


baconsmallnet <- t(baconsmallnet)
#View(baconsmallnet)
colnames(baconsmallnet) <- c("Score", "ID")

##merging bacon score to correct actor
mergedbacon <- merge(Actors_small, baconsmallnet, by="ID")
mergedbacon <- mergedbacon[,-1]
#View(mergedbacon)
#View(baconsmallnet)
colnames(baconsmallnet) <- c("Score", "ID")


mergedbacon <- merge(Actors_small, baconsmallnet, by="ID")
mergedbacon<- mergedbacon[,-1]

#View(mergedbacon)

```




```{r echo=FALSE, message=FALSE, warning=FALSE}

## formating interactive tables as a way to view bacon scores 
library(reactable)
#install.packages("reactablefmtr")
library(reactablefmtr)

reactable(mergedbacon, filterable = TRUE, minRows = 1) %>% add_title("Steps Away From Tom Hanks aka Hanky Score", font_size=18, align="center")


## formating interactive tables as a way to view bacon scores 
reactable(baconhp, filterable = TRUE, minRows = 1) %>% add_title("Steps Away From Harry Potter", font_size=18, align="center")

```


```


## A few concluding points :


-To our surprise, there are fewer connections between actors in the top 1000 movies than anticipated. This could be due to time range or even just the diverse pool of actors that we have today.

-As we saw in the Harry Potter example, we can visualize a more cohesive network when there are more connections present. 

-Additionally, the connectivity score in the Harry Potter network were no score of infinity like in the actors data set. This tells us that everyone in the Harry Potter data set is somehow connected to Harry Potter. This is not the case within the actors data set, meaning not everyone is connected to Tom Hanks even if they do have more than one connection. 

-In general, interactiveness allows for more in depth exploration while also not causing things (plots or networks) to appear overcrowded. 




